---
title: "Carte Golfe du St Laurent & St Pierre et Miquelon"
author: "A. Boyé"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  github_document:
    toc: true
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = TRUE, eval = TRUE, cache = TRUE)
```

---

# Packages {.tabset}

```{r packages}
library(ggplot2)
library(PBSmapping) 
library(data.table)
library(rgdal)
library(raster)
```

# Carte du monde centré sur le canada

```{r world_map}
world <- map_data("world")

worldmap <- ggplot(world, aes(x=long, y=lat, group=group)) 
worldmap <- worldmap + geom_path()
worldmap <- worldmap + scale_y_continuous(breaks=(-2:2) * 30) 
worldmap <- worldmap + scale_x_continuous(breaks=(-4:4) * 45)
worldmap <- worldmap + coord_map("ortho", orientation=c(44, -100, 0)) + ylab("") + xlab("")
worldmap <- worldmap + geom_polygon(data=world, mapping=aes(x=long, y=lat,group=group),col="gray45") 
worldmap <- worldmap + theme_light() + theme(axis.text=element_blank(),axis.ticks=element_blank(),panel.border=element_blank())

worldmap
```

---

# Carte zoomée sur Golfe du Saint Laurent 

```{r st_laurent}
world <- map_data("world")

setnames(world,c("X","Y","PID","POS","region","subregion"))

xlim <- c(-70,-40)
ylim <- c(40,60)

worldmap <- clipPolys(world, xlim=xlim,ylim=ylim, keepExtra=TRUE)

p <- ggplot() 
p <- p + coord_map(xlim=xlim,ylim=ylim) 
p <- p + geom_polygon(data=worldmap,aes(X,Y,group=PID))
p <- p + theme_bw() + theme(panel.background = element_rect(fill = "aliceblue", colour = "grey"),panel.grid.major = element_line(colour = "gray90",size=.7),panel.border=element_blank())

p
```

---

# Carte zoomée sur St Pierre

## Version `maps`

```{r st_pierre_maps}

world <- map_data("world")

setnames(world,c("X","Y","PID","POS","region","subregion"))

xlim <- c(-56.5,-55.5)
ylim <- c(46.5,47.3)

worldmap <- clipPolys(world, xlim=xlim,ylim=ylim, keepExtra=TRUE)


p <- ggplot() 
p <- p + coord_map(xlim=xlim,ylim=ylim) 
p <- p + geom_polygon(data=worldmap,aes(X,Y,group=PID))
p <- p + theme_bw() + theme(panel.background = element_rect(fill = "aliceblue", colour = "grey"),panel.grid.major = element_line(colour = "gray90",size=.7),panel.border=element_blank())

p
```

## Version `Openstreetmap`

### Crop Openstreetmap polygon layer

`land_polygons` was downloaded from openstreetmapdata.com which offers
extracts and processings of OpenStreetMap data. 

See http://openstreetmapdata.com/ for details.

Layers contained are:

land_polygons.shp:

  598199 Polygon features
  WGS84 geographic coordinates
  Extent: (-180.000, -90.000) - (180.000, 83.666)

Date of the data used is 28 Oct 2017 04:45

You can find more information on this data set at

http://openstreetmapdata.com/data/land-polygons

> ### LICENSE
> This data is Copyright 2017 OpenStreetMap contributors. It is
available under the Open Database License (ODbL).
>
> For more information see http://www.openstreetmap.org/copyright

This layer being to heavy, it was not included in this Github repository, only the cropped layer is. To crop the intial layer, the following code was used.

```{r poly_crop, eval = FALSE}
# Read land_polygons.shp from the current working directory (".")
poly_layer <- readOGR(dsn=".",layer = "land_polygons")

# Crop the layer to the desired extent
poly_layer_cropped <- crop(poly_layer,extent(-56.5,-55.5,46.5,47.3))

# Save the cropped layer
writeOGR(poly_layer_cropped, ".", "land_polygons_cropped", driver="ESRI Shapefile")
```

### Map with the cropped layer

```{r st_pierre_openstreetmap, message = FALSE}

# Read land_polygons.shp from the current working directory (".")
poly_layer <- readOGR(dsn=".",layer = "land_polygons_cropped")

# Project the layer in WGS84 (if you want to change projection)
poly_proj <- spTransform(poly_layer, CRS("+init=epsg:4326"))

p <- ggplot() 
p <- p + geom_polygon(data=poly_proj,aes(long,lat,group=id),col="gray45") 
p <- p + theme_bw() + theme(panel.background = element_rect(fill = "aliceblue", colour = "grey"),panel.grid.major = element_line(colour = "gray90",size=.7),panel.border=element_blank())
p

```

---

# Session info

```{r session_info}
sessionInfo()
```
